A free/open-source Kazakh-Tatar machine translation system

### 2013-06-30 paper/paper.tex
version submitted as final, though we still have a few things left to work on

%FIXME NOW
All evaluation was tested against version 0.1.0, or {\tt {\small rNNNNNN}} in the Apertium SVN.\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/trunk/apertium-kaz-tat}}
%The versions of the transducers tested were {\tt {\small r43595}} from the Apertium SVN.\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/staging/apertium-kaz-tat}}

@@

The system is available as free/open-source software under the GNU GPL and the whole system may be downloaded
from SVN.\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/trunk/apertium-kaz-tat}}

>>>>

%FIXME NOW
All evaluation was tested against version 0.1.0, or {\tt {\small r45441}} in the Apertium SVN.\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/staging/apertium-kaz-tat}}
%The versions of the transducers tested were {\tt {\small r43595}} from the Apertium SVN.\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/staging/apertium-kaz-tat}}

@@

The system is available as free/open-source software under the GNU GPL and the whole system may be downloaded
from SVN.\footnote{\url{https://apertium.svn.sourceforge.net/svnroot/apertium/staging/apertium-kaz-tat}}
